Dirac neutrino mass generation from Majorana messenger

### 2019-09-18 draft.tex
lc

With the aim of thermalize the right-handed neutrinos we consider an extension of the previous setup by introducing a general Abelian gauge symmetry $\operatorname{U(1)}_X$ with generation-independent charge assignments for the SM fields. Extra chiral fields are required to cancel the anomalies for solutions beyond the one proportional to $\operatorname{U}(1)_Y$. In the appendix we show that the solutions to the anomaly cancellation conditions parameterized in terms
of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc}, can be normalized to depend in just one parameter~\cite{Jenkins:1987ue,Oda:2015gna,Okada:2018tgy} that we choose to be the $X$-charge of the lepton doublet as displayed in column $\operatorname{U}(1)_X$ of Table~\ref{tab:partcont3}.
There, the previous dark symmetry denoted as $X=\mathcal{D}$ corresponds to the fermiophobic setup~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.

@@

In order to analyse the phenomenology we fix $l$ to recover some already studied
Abelian gauge groups $X=B-L,R,D,G,$ as defined in Ref.~\cite{Campos:2017dgc}\footnote{We change $\operatorname{U}(1)_B$ for the more suitable name of $\operatorname{U}(1)_R$~\cite{Jana:2019mez}.}.

>>>>

With the aim of thermalize the right-handed neutrinos with the
primordial plasma in the early universe, we consider an extension of
the previous setup by introducing a general anomaly free Abelian gauge
symmetry with generation-independent charge assignment for the
standard model fermions, $\operatorname{U}(1)_{X}$.
% 
In the appendix we show that the solutions to the anomaly cancellation conditions
allow us to write the $X$-charges of the SM fields in terms
of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc}, that we choose as
\begin{align}
  X(r,l)=r R - l Y\,,
\end{align}
where $R$ is the generator of $\operatorname{U}(1)_R$: the gauge Abelian symmetry where only the right-handed SM fields have non-vanishing $X$-charges, $Y$ is the hypercharge, $l$ is the $X$-charge of the lepton doublets, and $r$ parametrize the contribution to the linear and mixed gauge-gravitational anomalies of any extra set of chiral fermions, as given in eq.~\eqref{eq:anolam}.
In this way, if only extra vector-like fermions are allowed beyond the SM ($r=0$) the solution must be proportional to hypercharge.
%
Without lost of generality, we can write the solutions in terms of just one parameter~\cite{Jenkins:1987ue,Oda:2015gna,Okada:2018tgy}, that we choose to be $l$  after fix $r=1$. Then, as shown in the Appendix, the full family of solutions for fixed $l$ can be obtained after  rescaling all the $X$-charges by a factor $r$. In particular, the fermiophobic~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf} solution used in the previous sections, $\operatorname{U}(1)_{\mathcal{D}}$, corresponds to the rescaling $r=0$ of the $\operatorname{U}(1)_R$ solution.

The one parameter solution is shown in  column $\operatorname{U}(1)_X$
of Table~\ref{tab:partcont3}.
In order to analyse the phenomenology we fix $l$ to recover some already studied
Abelian gauge groups $X=B-L,R,D,G,$ as defined in Ref.~\cite{Campos:2017dgc}\footnote{We change $\operatorname{U}(1)_B$ for the more suitable name of $\operatorname{U}(1)_R$~\cite{Jana:2019mez}.}. The last column can be obtained after a reescaling with $r=0$ of $\operatorname{U}(1)_R$.

@@
